Network Data Collection for Artifical Intelligence

### 2020-02-28 paper2/paper2.tex
Update paper2.tex

With the wide set of options, \textit{tcpdump} is a pretty agile tool for dumping any analysing network traffic. A few of the options are listed below \cite{wikiUbuntu}.

@@

For the Windows enthusiasts a Windows derivative of \textit{tcpdump} is available. It is called \textit{WinDump}. \textit{WinDump} uses so called WinPcap library for Windows operating systems.  Which has the same APIs as libpcap for Unix-like systems. This means, network traffic captured, e.g. on a Ubuntu system can be analysed on a Windows 10 Client afterwards.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.30]{capsa.png}}
\caption{Graphical Evaluation of Network Traffic with Capsa}
\label{capsa}
\end{figure}

@@

\bibitem{wikiUbuntu} ubuntuusers.de
\bibitem{asrodiapatel2012} P. Asrodia, H. Patel (2012). Analysis  of  Various  Packet  Sniffing  Tools  for Network  Monitoring  and  Analysis.
\bibitem{suribatra2012} S. Suri, V. Batra, Comparative Study of Network Monitoring Tools.

>>>>

With the wide set of options, \textit{tcpdump} is a pretty agile tool for dumping any analysing network traffic. A few of the options are listed below \cite{tcpdumporg}.

@@

If \textit{tcpdump} is compiled with cryptography, it is able to decrypt IPsec ESP packets in real time \cite{goyal2017}.
For the Windows enthusiasts a Windows derivative of \textit{tcpdump} is available. It is called \textit{WinDump}. \textit{WinDump} uses so called WinPcap library for Windows operating systems.  Which has the same APIs as libpcap for Unix-like systems. This means, network traffic captured, e.g. on a Ubuntu system can be analysed on a Windows 10 Client afterwards.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.30]{capsa.png}}
\caption{Graphical Evaluation of Network Traffic with Capsa \cite{firewallcx}}
\label{capsa}
\end{figure}

@@

\bibitem{tcpdumporg} Van Jacobson, C. Leres, S. McCanne,tcpdump.org (26.02.2020) https://www.tcpdump.org/manpages/tcpdump.1.html [Accessed 27.02.2020]
\bibitem{asrodiapatel2012} P. Asrodia, H. Patel (2012). Analysis  of  Various  Packet  Sniffing  Tools  for Network  Monitoring  and  Analysis, ISSN  No.  (Online)  :  2277-2626
\bibitem{suribatra2012} S. Suri, V. Batra, Comparative Study of Network Monitoring Tools, International Journal ofInnovative Technology and Exploring Engineering (IJITEE)ISSN: 2278-3075,Volume-1, Issue-3, August 2012
\bibitem{goyal2017} P. Goyal, A. Goyal (2017), Comparative study of two most popular packet sniffing tools-Tcpdump and Wireshark
\bibitem{firewallcx} http://www.firewall.cx/images/stories/review-capsa-enterprisev7-7.jpg [Accessed 26.02.2020]
